Fourmile Calibrations

### 2023-02-06 calibration_output.Rmd
facet plots are small..
updated max Q prior to Apr 1 to be for March only, fixed teh facet wrap small plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

@@

ensem_bould <- left_join(ensem, bouldcr, by = 'date') %>%
  pivot_longer(!c(date, year), names_to = 'source', values_to = 'q_m3s') %>%
  mutate(month = month(date)) %>%
  filter(month %in% 1:3) %>%
  group_by(source, year) %>%
  slice_max(q_m3s, n=1)

@@

ggplot(early_peakq, aes(doy_bouldcr, doy_all_ensemble)) +
  geom_point(size=2.5) +
  geom_abline(intercept = 0, slope = 1, size=1, color='red') +
  theme_bw() +
  ggtitle('DOY of peak Q prior to April 1st - All Ensemble')

ggplot(early_peakq, aes(doy_bouldcr, doy_grid_all)) +
  geom_point(size=2.5) +
  geom_abline(intercept = 0, slope = 1, size=1, color='red') +
  theme_bw() +
  ggtitle('DOY of peak Q prior to April 1st - Grid All')

ggplot(early_peakq, aes(doy_bouldcr, doy_grid_ensemble)) +
  geom_point(size=2.5) +
  geom_abline(intercept = 0, slope = 1, size=1, color='red') +
  theme_bw() +
  ggtitle('DOY of peak Q prior to April 1st - Grid Ensemble')

ggplot(early_peakq, aes(doy_bouldcr, doy_statn_all)) +
  geom_point(size=2.5) +
  geom_abline(intercept = 0, slope = 1, size=1, color='red') +
  theme_bw() +
  ggtitle('DOY of peak Q prior to April 1st - Station All')

ggplot(early_peakq, aes(doy_bouldcr, doy_statn_ensemble)) +
  geom_point(size=2.5) +
  geom_abline(intercept = 0, slope = 1, size=1, color='red') +
  theme_bw() +
  ggtitle('DOY of peak Q prior to April 1st - Station Ensemble')

@@

```{r rd and rg, echo = F}

@@

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=genRD1)) +
  facet_wrap(~year, scales = 'free') +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('genRD1')

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=genRD2)) +
  facet_wrap(~year, scales = 'free') +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('genRD2')

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=genRG1)) +
  facet_wrap(~year, scales = 'free') +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('genRG1')

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=genRG2)) +
  facet_wrap(~year, scales = 'free') +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('genRG2')

@@

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD1cumsum)) +
  facet_wrap(~year, scales = 'free') +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative genRD1')

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD2cumsum)) +
  facet_wrap(~year, scales = 'free') +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative genRD2')

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG1cumsum)) +
  facet_wrap(~year, scales = 'free') +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative genRG1')

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG2cumsum)) +
  facet_wrap(~year, scales = 'free') +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative genRG2')

@@

# HRU Map

@@

# Niwot and HRU7

## SWE and precip

```{r niwot, echo = F}
library(snotelr)

@@

cum_swe_niwot <- ggplot(niwot_swe2, aes(date, swe_cumsum_mm, color = source)) +
  geom_line() +
  scale_x_date(labels = date_format("%b")) +
  facet_wrap(~year, scales = 'free')

@@

cum_precip_niwot <- ggplot(niwot_p2, aes(date, p_cumsum_mm, color = source)) +
  geom_line() +
  scale_x_date(labels = date_format("%b")) +
  facet_wrap(~year, scales = 'free')

@@

## ET

@@

# Tmean for HRUs 7, 9, 22, 36

```{r hru7 temp, echo = F}

@@

tmean_cumdiff_plot <- ggplot(t_hrus, aes(x = date)) +
  geom_line(aes(y = t7_cumdiff, color = 'HRU7'), size =1) + 
  geom_line(aes(y = t9_cumdiff, color = 'HRU9'), size =1) + 
  geom_line(aes(y = t22_cumdiff, color = 'HRU22'), size =1) + 
  geom_line(aes(y = t36_cumdiff, color = 'HRU36'), size =1) + 
  facet_wrap(~year, scales = 'free') +
  scale_x_date(labels = date_format("%b")) +
  labs(y = 'Tmean cumulative difference (deg C)') +
  ggtitle('Tmean station and grid cumulative difference (Station - Grid)')

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F)

@@

ensem_bould <- left_join(ensem, bouldcr, by = 'date') %>%
  pivot_longer(!c(date, year), names_to = 'source', values_to = 'q_m3s') %>%
  mutate(month = month(date)) %>%
  filter(month %in% 3) %>%
  group_by(source, year) %>%
  slice_max(q_m3s, n=1)

@@

marpeakq <- ggplot(early_peakq, aes(x = doy_bouldcr)) +
  geom_point(aes(y = doy_all_ensemble, shape = "all_ensemble"), size=2.5) +
  geom_point(aes(y = doy_grid_all, shape = 'grid_all'), size=2.5) +
  geom_point(aes(y = doy_grid_ensemble, shape = 'grid_ensemble'), size=2.5) +
  geom_point(aes(y = doy_statn_all, shape = 'statn_all'), size=2.5) +
  geom_point(aes(y = doy_statn_ensemble, shape = 'statn_ensemble'), size=2.5) +
  geom_abline(intercept = 0, slope = 1, size=1, color='red') +
  labs(x = "Boulder Creek DOY for March Peak Q", y = 'DOY for March Peak Q') +
  theme_bw() +
  scale_shape_manual(name="source", values=c("all_ensemble"=15, 
                                            "grid_all"=16, 
                                            "grid_ensemble"=17,
                                            "statn_all"=18, 
                                            "statn_ensemble" = 8))+
  ggtitle('DOY of peak Q in March')

ggplotly(marpeakq)

# ggplot(early_peakq, aes(doy_bouldcr, doy_grid_all)) +
#   geom_point(size=2.5) +
#   geom_abline(intercept = 0, slope = 1, size=1, color='red') +
#   theme_bw() +
#   ggtitle('DOY of peak Q prior to April 1st - Grid All')
# 
# 
# ggplot(early_peakq, aes(doy_bouldcr, doy_grid_ensemble)) +
#   geom_point(size=2.5) +
#   geom_abline(intercept = 0, slope = 1, size=1, color='red') +
#   theme_bw() +
#   ggtitle('DOY of peak Q prior to April 1st - Grid Ensemble')
# 
# 
# ggplot(early_peakq, aes(doy_bouldcr, doy_statn_all)) +
#   geom_point(size=2.5) +
#   geom_abline(intercept = 0, slope = 1, size=1, color='red') +
#   theme_bw() +
#   ggtitle('DOY of peak Q prior to April 1st - Station All')
# 
# 
# ggplot(early_peakq, aes(doy_bouldcr, doy_statn_ensemble)) +
#   geom_point(size=2.5) +
#   geom_abline(intercept = 0, slope = 1, size=1, color='red') +
#   theme_bw() +
#   ggtitle('DOY of peak Q prior to April 1st - Station Ensemble')

@@

```{r rd and rg, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"}

@@

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=genRD1), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('genRD1') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=genRD2), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('genRD2') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=genRG1), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('genRG1') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=genRG2), size =1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('genRG2') +
  theme(text = element_text(size = 20))

@@

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD1cumsum), size =1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative genRD1') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD2cumsum), size = 1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative genRD2') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG1cumsum), size  = 1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative genRG1') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG2cumsum), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative genRG2') +
  theme(text = element_text(size = 20))

@@

# HRU results

## HRU Map

@@

## Niwot and HRU7

### SWE and precip

```{r niwot, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"}
library(snotelr)

@@

cum_swe_niwot <- ggplot(niwot_swe2, aes(date, swe_cumsum_mm, color = source)) +
  geom_line(size =1) +
  scale_x_date(labels = date_format("%b")) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  theme(text = element_text(size = 20))

@@

cum_precip_niwot <- ggplot(niwot_p2, aes(date, p_cumsum_mm, color = source)) +
  geom_line(size=1) +
  scale_x_date(labels = date_format("%b")) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  theme(text = element_text(size = 20))

@@

### ET

@@

## Tmean for HRUs 7, 9, 22, 36

```{r hru7 temp, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"}

@@

tmean_cumdiff_plot <- ggplot(t_hrus, aes(x = date)) +
  geom_line(aes(y = t7_cumdiff, color = 'HRU7'), size =1) + 
  geom_line(aes(y = t9_cumdiff, color = 'HRU9'), size =1) + 
  geom_line(aes(y = t22_cumdiff, color = 'HRU22'), size =1) + 
  geom_line(aes(y = t36_cumdiff, color = 'HRU36'), size =1) + 
  facet_wrap(~year, scales = 'free',ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  labs(y = 'Tmean cumulative difference (deg C)') +
  ggtitle('Tmean station and grid cumulative difference (Station - Grid)') +
  theme(text = element_text(size = 20))
